% Peter Williams' LaTeX template for a list of publications.
% This work is dedicated to the public domain.

\documentclass[letterpaper,11pt]{article}

% Basic settings for your convenience!

\newcommand{\myname}{Eric W. Koch}
\newcommand{\mysite}{e-koch.github.io}

% Here begins a ton of boilerplate to set up the document to look nice.
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% margins
\usepackage[margin=0.5in,bottom=0.75in]{geometry}

% nice links
\usepackage[colorlinks,urlcolor=blue]{hyperref}
\urlstyle{sf}

% needed for the fancy footer
\usepackage{fancyhdr,lastpage}

% layout of the publication list
\usepackage{enumitem}
\newenvironment{publist}{
  \begingroup
  \raggedright
  \begin{description}[leftmargin=4ex,style=sameline]
}{
  \end{description}
  \endgroup
}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% That's the end of the boilerplate. Now come some things that don't involve
% any templating.

\begin{document}

% running footer
\pagestyle{fancy}
\lhead{} \chead{} \rhead{} \renewcommand{\headrule}{\relax}
\lfoot{\textsc{List of Publications}}
\cfoot{\thepage/\pageref*{LastPage}}
\rfoot{\textsc{\myname}}

% title
\begin{center}
\textbf{\Large \myname} \\
{\large Publications}
\end{center}


% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Here's where we actually start using the templates.

\noindent Updated % note: must have this awkward newline for the simpleminded templater:
Sep 26, 2019.
% The most recent version of this list may be found online at
% \url{\mysite}.
\href{http://labs.adsabs.harvard.edu/adsabs}{ADS} citation counts are shown in square brackets and were last updated
around Sep 26, 2019. As of then, I was an author on 10
refereed publications (6 as first author), my \textit{h}-index was
6 and my refereed publications had 117 citations.



% \section*{Submitted}

% \begin{publist}
% PUBLIST refpreprint_rev
% \end{publist}

\section*{Refereed}

\begin{publist}
\item[10.] \textbf{EW Koch}, EW Rosolowsky, RD Boyden, B Burkhart, A Ginsburg, JL Loeppky, SSR Offner. \textit{``TurbuStat: Turbulence Statistics in Python.''} 2019, \href{http://adsabs.harvard.edu/abs/2019AJ....158....1K}{AJ 158 1} [1].
\item[9.] \textbf{EW Koch}, EW Rosolowsky, A Schruba, A Leroy, AA Kepley, J Braine, J Dalcanton, MC Johnson. \textit{``Relationship between the Line Width of the Atomic and Molecular ISM in M33.''} 2019, \href{http://adsabs.harvard.edu/abs/2019MNRAS.485.2324K}{MNRAS 485 2324} [1].
\item[8.] \textbf{EW Koch}, EW Rosolowsky, FJ Lockman, AA Kepley, A Leroy, A Schruba, J Braine, J Dalcanton, MC Johnson, S Stanimirovi\'{c}. \textit{``Kinematics of the atomic ISM in M33 on 80 pc scales.''} 2018, \href{http://adsabs.harvard.edu/abs/2018MNRAS.479.2505K}{MNRAS 479 2505-2533} [6].
\item[7.] RD Boyden, SSR Offner, \textbf{EW Koch}, EW Rosolowsky. \textit{``Assessing the Impact of Astrochemistry on Molecular Cloud Turbulence Statistics.''} 2018, \href{http://adsabs.harvard.edu/abs/2018ApJ...860..157B}{ApJ 860 157} [4].
\item[6.] \textbf{EW Koch}, CG Ward, S Offner, J Loeppky, E Rosolowsky. \textit{``Identifying Tools for Comparing Simulations of Star Formation.''} 2017, \href{http://adsabs.harvard.edu/abs/2017MNRAS.471.1506K}{MNRAS 471 1506-1530} [9].
\item[5.] Y Lin, HB Liu, JE Dale, D Li, G Busquet, ZY Zhang, A Ginsburg, R Galvan-Madrid, A Kovacs, \textbf{E Koch}, L Qian, K Wang, S Longmore, HR Chen, D Walker. \textit{``Cloud Structure of Three Galactic Infrared Dark Star-forming Regions from Combining Ground- and Space-based Bolometric Observations.''} 2017, \href{http://adsabs.harvard.edu/abs/2017ApJ...840...22L}{ApJ 840 22} [13].
\item[4.] RD Boyden, \textbf{EW Koch}, EW Rosolowsky, SSR Offner. \textit{``An Exploration of the Statistical Signatures of Stellar Feedback.''} 2016, \href{http://adsabs.harvard.edu/abs/2016ApJ...833..233B}{ApJ 833 233} [9].
\item[3.] Y Lin, HB Liu, D Li, Z-Y Zhang, A Ginsburg, JE Pineda, L Qian, R Galv\'{a}n-Madrid, AF McLeod, E Rosolowsky, JE Dale, K Immer, \textbf{E Koch}, S Longmore, D Walker, L Testi. \textit{``Cloud Structure of Galactic OB Cluster-forming Regions from Combining Ground and Space-based Bolometric Observations.''} 2016, \href{http://adsabs.harvard.edu/abs/2016ApJ...828...32L}{ApJ 828 32} [21].
\item[2.] \textbf{EW Koch}, EW Rosolowsky. \textit{``Filament Identification through Mathematical Morphology.''} 2015, \href{http://adsabs.harvard.edu/abs/2015MNRAS.452.3435K}{MNRAS 452 3435-3450} [49].
\item[1.] \textbf{EW Koch}, A Bahramian, CO Heinke, K Mori, N Rea, N Degenaar, D Haggard, R Wijnands, G Ponti, JM Miller, F Yusef-Zadeh, F Dufour, WD Cotton, FK Baganoff, MT Reynolds. \textit{``The 2013 outburst of a transient very faint X-ray binary, 23 arcsec from Sgr A\textasteriskcentered.''} 2014, \href{http://adsabs.harvard.edu/abs/2014MNRAS.442..372K}{MNRAS 442 372-381} [4].
\end{publist}

\section*{Submitted}

\begin{publist}
\item[1.] CO Heinke, MG Ivanov, \textbf{EW Koch}, R Andrews, L Chomiuk, HN Cohn, S Crothers, T Boer, N Ivanova, AKH Kong, N Leigh, PM Lugger, L Nelson, CJ Parr, EW Rosolowsky, AJ Ruiter, CL Sarazin, AW Shaw, GR Sivakoff, M Berg. \textit{``The X-ray Emissivity of Low-Density Stellar Populations.''} 2019, \href{http://adsabs.harvard.edu/abs/None}{MNRAS submitted}.
\end{publist}

\section*{Non-Refereed}

\begin{publist}
\item[2.] \textbf{E Koch}, E Rosolowsky, AK Leroy. \textit{``Radio-line Broadening from a Spectral Response Function.''} 2018, \href{http://adsabs.harvard.edu/abs/2018RNAAS...2d.220K}{RNAAS 2 220} [1].
\item[1.] \textbf{E Koch}, E Rosolowsky, MC Johnson, AA Kepley, A Leroy. \textit{``Detection of an OH 1665 MHz Maser in M33.''} 2018, \href{http://adsabs.harvard.edu/abs/2018RNAAS...2a..24K}{RNAAS 2 24} [1].
\end{publist}


\end{document}
